---
title: "Desert Rose"
subtitle: "Desertification in Niger"
author: "Aaron, Andro, Huan, James, Maria, Sameera"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r echo = FALSE, message = FALSE, warning = FALSE}
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
library(readxl)
library(fs)
library(countdown)
library(xaringan)
library(xaringanExtra)
library(knitr)

hook_source <- knitr::knit_hooks$get('source')
knitr::knit_hooks$set(source = function(x, options) {
  x <- stringr::str_replace(x, "^[[:blank:]]?([^*].+?)[[:blank:]]*#<<[[:blank:]]*$", "*\\1")
  hook_source(x, options)
})

xaringanExtra::use_broadcast()
xaringanExtra::use_freezeframe()
xaringanExtra::use_scribble()
#xaringanExtra::use_slide_tone()
xaringanExtra::use_search(show_icon = TRUE, auto_search	=FALSE)
xaringanExtra::use_freezeframe()
xaringanExtra::use_clipboard()
xaringanExtra::use_tile_view()
xaringanExtra::use_panelset()
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_fit_screen()
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         
  mute_unhighlighted_code = TRUE  
)

```

---



---
# Visualisation of Impacts/Risks

.panelset[
.panel[.panel-name[Extreme Heat]
```{r echo=FALSE}
#read in images here
```

]
.panel[.panel-name[Water Body Loss]
```{r echo=FALSE}
#read in images here
```

]
]

---
# Justification behind Niger


---
# Definition of Desertification


---
# Niger’s vast potential to turn things around with GGW


---
# Systematic challenges hindering GGW

---
# Our contributions


---
# Methodology Framework

---
# Workflow Phase 1


---
# Workflow Phase 2


---
# Earth Observation Data


---
# Additional Data


---
# Sample Dashboard Preview


---
# Sample Dashboard Demo


---
# Limitations


---
# Recommended Action Plans


---
# Project Timeline



---
# Project Costing



---


# References



---

class: center, middle

# Thank You

